\documentclass[../main_corrected.tex]{subfiles}
\begin{document}

\section{Risk-Aware Pro-Rata (RAP)}\label{app:rap}
\input{main_examples.tex}

\subsection{RAP Optimality and Convex Dominance}\label{app:rap-optimality-and-convex-dominance}\label{sec:rap-optimality-and-convex-dominance}
In this appendix, we prove two statements: 1) RAP optimizes the one-step next deficit~\eqref{eq:delta-T} and 2) RAP has a smaller residual than any other comonotone haircut rule.

\iparagraph{RAP optimizes $\delta_T$.}
In this section, we briefly show that RAP optimizes the one-step deficit proxy $\delta_T$.
We do this by showing that the weights determined by the perspective transformr $\rho(\lambda)$, which define $g^{\star}$, optimize $\delta_T$.

\begin{proposition}\label{thm:rap-onestep-7}
Fix a round $t$ with budget $b_t=\theta_t|D_t|$ and per‑account caps $0\le H_{t,i}\le 1$. For
\[
\delta_t(h)=\sum_{i\in W_t} (1-h_{t,i})\,\lambda_{t,i}e_{t,i}\,\psi_i\!\Big(\tfrac{1}{\lambda_{t,i}}\Big)
\]
the capped reverse-\-waterfilling with risk weights $\tilde{w}_{t,i}=\rho(\lambda_{t,i})=\lambda_{t,i}\psi_i(1/\lambda_{t,i})$ minimizes $\delta_t(h)$ among all $h$ with $\sum_i w_{t,i}h_{t,i}=b_t$ and $0\le h_{t,i}\le H_{t,i}$, where $w_{t,i}$ is the haircutable endowment (under PNL-only, $w_{t,i}=(\mathrm{PNL}_{t,i})_+$).
\end{proposition}
\begin{proof}
Using $\rho(\lambda)=\lambda\psi(1/\lambda)$,
\[
\delta_t(h)=\sum_i (1-h_{t,i})\,\lambda_{t,i}e_{t,i}\,\psi(1/\lambda_{t,i})
\equiv C_h - \sum_i \rho(\lambda_{t,i}) e_{t,i} h_{t,i}
\]
where $C_h$ is a constant independent of $h$ (can depend on $\lambda_{t,i}$).
Note that $e_{t,i} = c_{t,i} + \mathrm{PNL}_{t,i}$ and under PNL-only haircuts, $w_{t,i} = (\mathrm{PNL}_{t,i})_+$.
The gradient $-\partial \delta_t / \partial x_{t,i}$ where $x_{t,i} = h_{t,i} w_{t,i}$ is $\rho(\lambda_{t,i}) e_{t,i}$ (expressed in equity terms because insolvency is an equity concept).
Maximizing $\sum_i \rho(\lambda_{t,i})\,e_{t,i} (x_{t,i}/w_{t,i})$ under $\sum_i x_{t,i}=b_t$ and $0\le x_{t,i}\le w_{t,i}H_{t,i}$ is a fractional knapsack problem solved by sorting the values $\rho(\lambda_{t,i}) e_{t,i}/w_{t,i}$.
The optimizer for this problem is reverse‑waterfilling~\cite{BoydVandenberghe2004}:
\[
h_{t,i}=\min\{H_{t,i},\ \tau^\star_t\,\tilde{w}_{t,i}\},\qquad \tilde{w}_{t,i}=\rho(\lambda_{t,i}),
\]
with $\tau^\star_t$ set by $\sum_i w_{t,i}h_{t,i}=b_t$. 
This choice of $\tilde{w}$ minimizes $\delta_t$ among all weighted reverse‑waterfilling rules.
\end{proof}

\iparagraph{RAP realizes Schur-convex dominance.}\label{app:lpr-convex-dominance}
We first note that theoretical results from the measure theoretic literature imply than RAP should provide Schur-convex dominance.
RAP weights $w_i = \lambda_{T,i} g(\lambda_{T,i})$ can be interpreted as allocating budget proportional to a coherent, law-invariant risk measure.
Specifically, let $\rho(\lambda) = \lambda\,\psi(1/\lambda)$ be a risk density with $\psi$ convex and nonincreasing.
This corresponds to a spectral risk measure $\rho(X) = \int_0^1 \mathrm{ES}_\alpha(X)\,d\mu(\alpha)$ via the Kusuoka representation~\citep{Kusuoka2001,Acerbi2002}.
Choosing $g(\lambda) = \rho(\lambda)/\lambda$ aligns the RAP allocation with this spectral density.
Known results from~\cite{Kusuoka2001} then imply RAP with a ``more convex'' risk density (in the Schur sense) will weakly Schur-dominate any other weighted pro-rata rule with a less concentrated density.
Instead of utilizing such strong measure theoretic tools, we instead prove this directly below in an elementary manner.

\begin{theorem}[Constructive Schur–convex dominance]\label{thm:rho-to-g-dominance}
Fix $T$, budget $b_T$, and caps $(\beta_i)$. Let $\rho$ be nondecreasing and $g^\star(\lambda)=\rho(\lambda)/\lambda$.
Consider any weighted pro-rata rule $h^{(w)}$ with weights $w$.
If the haircut share vector of $h^{(w)}$ is no more concentrated on high-$\rho$ indices than that of $\mathrm{RAP}(g^\star)$ on any fixed active set, then the residual vector of $\mathrm{RAP}(g^\star)$ weakly submajorizes that of $h^{(w)}$:
\[
z_T(\mathrm{RAP}(g^\star)) \preceq_w z_T(h^{(w)}).
\]
Thus, for any convex increasing $\phi$, $\sum \phi(z_{T,i}(\mathrm{RAP})) \le \sum \phi(z_{T,i}(h^{(w)}))$.
\end{theorem}

\begin{proof}
We split this proof into three steps.
The first step is analogous to the proof of Proposition~\ref{thm:unique-pro-rata}, where we analyze the change to the weights on a piecewise constant set of intervals.
The second step is to analyze how the residuals change with budget using the piecewise-constant representation.
Given the change in residual, the final step uses the majorization inequality to show that the residual vector of RAP weakly submajorizes that of any other weighted pro-rata rule.

\emph{Step 1: Active set and parameterization.}
We first define the active set $A(b)$ as in~\eqref{eq:active-set}.
Any weighted reverse‑waterfilling with risk weights $\tilde{w}$ admits the water‑level form
\[
  h^{(\tilde{w})}_{T,i}(b)\;=\;\min\{\beta_i,\ \tau^{(\tilde{w})}(b)\,\tilde{w}_i\},
\]
where $\tau^{(\tilde{w})}(b)$ is chosen so that $\sum_i w_{T,i}\,h^{(\tilde{w})}_{T,i}(b)=b$ (budget constraint in endowment space).
On an interval $[b_0,b_1]$ with fixed $A(b)$ we have
\[
  \frac{db}{d\tau^{(\tilde{w})}}=\sum_{j\in A(b)} w_{T,j} \tilde{w}_j,
  \qquad
  \frac{d h^{(\tilde{w})}_{T,i}}{db}
  \;=\;
  \begin{cases}
    \displaystyle \frac{\tilde{w}_i}{\sum_{j\in A(b)} w_{T,j} \tilde{w}_j},& i\in A(b),\\[1.0ex]
    0,& i\notin A(b).
  \end{cases}
\]
\emph{Step 2: Residual dynamics.}
Next we look at how the residuals (\eg~post haircut equity) change with budget.
Write the reweighted residuals as
\[
  z_{T,i}(b)\;=\;\rho(\lambda_{T,i})\,e_{T,i}\,\bigl(1-h_{T,i}(b)\bigr),
\]
where the equity $e_{T,i}$ appears because insolvency is an equity concept, but the control variable is the endowment $w_{T,i}$ via $h_{T,i}$.
Then on $[b_0,b_1]$,
\[
  \frac{d z^{(\tilde{w})}_{T,i}}{db}
  \;=\;
  \begin{cases}
    \displaystyle -\frac{\rho(\lambda_{T,i})\,e_{T,i}\,\tilde{w}_i}{\sum_{j\in A(b)} w_{T,j} \tilde{w}_j},& i\in A(b),\\[1.0ex]
    0,& i\notin A(b).
  \end{cases}
\]
For $\mathrm{RAP}(g^\star)$ we take $\tilde{w}_i=\rho(\lambda_{T,i})$, giving
\[
  \frac{d z^{(\mathrm{RAP})}_{T,i}}{db}
  \;=\;
  \begin{cases}
    \displaystyle -\frac{\rho(\lambda_{T,i})^2\,e_{T,i}}{\sum_{j\in A(b)} w_{T,j} \rho(\lambda_{T,j})},& i\in A(b),\\[1.0ex]
    0,& i\notin A(b).
  \end{cases}
\]
\emph{Step 3: Majorization at each budget.} On a fixed $A(b)$, sort indices by decreasing $\rho(\lambda_{T,i})$.
By the hypothesis that the haircut share vector of $h^{(\tilde{w})}$ on $A(b)$,
\[
  \sigma^{(\tilde{w})}_i(b)\ :=\ \frac{w_{T,i} \tilde{w}_i}{\sum_{j\in A(b)} w_{T,j} \tilde{w}_j},
\]
is no more concentrated on high‑$\rho$ indices than the RAP share
$\sigma^{(\mathrm{RAP})}_i(b)=\frac{w_{T,i} \rho(\lambda_{T,i})}{\sum_{j\in A(b)} w_{T,j} \rho(\lambda_{T,j})}$, the rearrangement/majorization inequality implies that for every $k$,
\[
  \sum_{i\le k}\!\frac{d z^{(\mathrm{RAP})}_{T,(i)}}{db}
  \;\leq\;
  \sum_{i\le k}\!\frac{d z^{(\tilde{w})}_{T,(i)}}{db}
\]
where $(i)$ denotes the order by decreasing $\rho$.
Hence the instantaneous decrease vector under RAP weakly submajorizes that under $h^{(\tilde{w})}$ on $[b_0,b_1]$.
Integrating over $b$ preserves $\prec_w$ on the interval, and concatenating the finitely many intervals where $A(b)$ changes preserves the order overall:
$z_T(\mathrm{RAP}(g^\star)) \preceq_w z_T(h^{(\tilde{w})})$.
Schur–convexity then yields the separable convex loss comparison.
\end{proof}

\input{ltv-example.tex}

\end{document}
